```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(xtable)
library(gsubfn)
library(fmtr)
library(stringr)
library(common)
library(proto)
library(patchwork)
library(forcats)
library(scales)
library(hash)
library(ggthemes)
library(ggsci)
library(egg)
library(grid)
library(RColorBrewer)
library(wesanderson)
library(ggpattern)
library(scales)
theme_set(theme_light())
"%!in%" <- function(x, y) !("%in%"(x, y)) # nolint: object_name_linter.
options(digits = 5, nsmall = 3)
```

Better plots: 
https://www.cedricscherer.com/2019/08/05/a-ggplot2-tutorial-for-beautiful-plotting-in-r/

Colors:
https://nanx.me/ggsci/articles/ggsci.html#introduction

Barchart pattern fill
https://coolbutuseless.github.io/2020/04/01/introducing-ggpattern-pattern-fills-for-ggplot/

Read the data

```{r wash_name}
wash_name <- function(t) {
  # NOTE: Wash data
  t$solver[t$solver == "test"] <- "Ours"
  t$solver[t$solver == "zdtree"] <- "ZdTree"
  t$solver[t$solver == "cgal"] <- "CGAL"
  t$solver[t$solver == "BHLtree"] <- "BhlTree"
  t$solver[t$solver == "Logtree"] <- "LogTree"
  return(t)
}
```

Main function for batchupdate

```{r}
# PERF: plot a subgraph
plot <- function(t, bench, title) {
  t <- wash_name(t)

  # NOTE: level
  nameLevel <- c("Ours", "ZdTree", "LogTree", "BhlTree", "CGAL")
  shapeLevel <- c(19, 17, 18, 20, 15)
  t$solver <- factor(t$solver, levels = nameLevel)

  t <- t %>%
    filter(dims == 3, benchType == bench) %>%
    select(-c(benchType, nodes, dims)) %>%
    pivot_longer(!solver, names_to = "BatchSize", values_to = "time")

  t$BatchSize <- factor(t$BatchSize, levels = unique(t$BatchSize))

  # NOTE: START PLOT
  g <- ggplot(t, aes(
    x = BatchSize, y = time, color = solver,
    shape = solver, group = solver
  )) +
    geom_point(size = 2, alpha = 0.8) + # point property
    geom_line() +
    labs(x = "Batch size", y = "time/sec (log-scale)") +
    scale_x_discrete(labels = c(
      "10%", "20%", "30%", "40%",
      "50%", "60%", "70%", "80%", "90%", "100%"
    )) +
    scale_y_log10() +
    scale_shape_manual(values = shapeLevel) +
    ggtitle(title) +
    theme(
      plot.margin = unit(c(.1, .01, .1, .01), "cm"),
      plot.title = element_text(hjust = 0.5, size = 9), # title size
      axis.text.x = element_text(angle = 30, size = 7), # axe size
      axis.title = element_text(margin = margin(0.5, 0.1, 0.1, 0.1), size = 8),
    ) +
    # coord_fixed(ratio = 1) +
    # scale_color_brewer(palette = "Set1")
    scale_color_locuszoom()
  # scale_color_npg()
  # scale_color_tableau()
  # scale_color_tableau("Classic 10 Medium")
  return(g)
}

# PERF: READ updates
ti <- read.csv("../data/insert.csv")
td <- read.csv("../data/delete.csv")
g <- plot(ti, "ss_varden", "Batch insertion on 3D-V-100M") +
  plot(ti, "uniform", "Batch insertion on 3D-U-100M") +
  plot(td, "ss_varden", "Batch deletion on 3D-V-100M") +
  plot(td, "uniform", "Batch deletion on 3D-U-100M") +
  plot_layout(guides = "collect")

ggsave("figures/batchupdate.pdf", width = 7, height = 5, dpi = 3600)
``````

Remove techniques

```{r remove techniques}
benchType <- c(
  rep("3D-U-100M / threads = 192", 4),
  rep("3D-U-100M / threads = 1", 4),
  rep("3D-V-100M / threads = 192", 4),
  rep("3D-V-100M / threads = 1", 4)
)
time <- c(
  5.640,
  4.293,
  2.444,
  1.000,
  1.735,
  2.124,
  0.986,
  1.000,
  5.102,
  3.964,
  2.457,
  1.000,
  1.728,
  2.171,
  0.985,
  1.000
)
ose <- "one layer + serial median"
op <- "one layer + parallel median"
osp <- "one layer + sample median"
ss <- "six layer + sample median"
techniques <- rep(c(ose, op, osp, ss))
t <- data.frame(benchType, techniques, time)
t$techniques <- factor(t$techniques, levels = c(ss, osp, op, ose))

# View(t)

plt <- ggplot(t, aes(y = time, x = benchType)) +
  # geom_bar(position = "dodge", stat = "identity") +
  # geom_bar_pattern(aes(fill = techniques), position = "dodge", stat = "identity") +
  geom_bar_pattern(
    aes(
      pattern = techniques,
      pattern_angle = techniques
    ),
    fill = "white",
    colour = "black",
    position = "dodge",
    stat = "identity",
    pattern_spacing = 0.025
  ) +
  theme(
    legend.position = c(0.18, 0.87),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14),
    plot.title = element_text(hjust = 0.5, size = 15),
    axis.text.x = element_text(size = 11), # axe size
    axis.text.y = element_text(size = 11), # axe size
    axis.title = element_text(size = 12)
  ) +
  labs(
    x = "Data size and threads number",
    y = "Normalized slow ratio",
    title = "Effectiveness of each technique",
    color = "techniques",
  ) +
  scale_y_continuous(breaks = c(0, 1, 4, 7, 10, 13)) +
  scale_fill_grey()
# scale_fill_manual(values = wes_palette("GrandBudapest2", n = 4, type = "discrete"))
# scale_fill_brewer("Techniques", palette = "Pastel1")

ggsave("figures/techniques.pdf", width = 10, height = 8, dpi = 1800)
``````


```{r knn}
plot <- function(t, bench, title) {
  t <- wash_name(t)
  colnames(t)[5] <- "k=1"
  colnames(t)[8] <- "k=10"
  colnames(t)[11] <- "k=100"
  nameLevel <- c("Ours", "ZdTree", "CGAL", "LogTree")
  t$solver <- factor(t$solver, levels = nameLevel)

  t <- t %>%
    filter(dims == 3, benchType == bench) %>%
    select(1, 5, 8, 11) %>%
    pivot_longer(!solver, names_to = "K", values_to = "time")

  t$K <- factor(t$K, levels = unique(t$K))

  plt <- ggplot(t, aes(y = time, x = K)) +
    geom_bar_pattern(
      aes(
        pattern = solver,
        pattern_angle = solver
      ),
      fill = "white",
      colour = "black",
      position = "dodge",
      stat = "identity",
      pattern_spacing = 0.025
    ) +
    theme(
      legend.position = c(0.18, 0.87),
      legend.text = element_text(size = 12),
      legend.title = element_text(size = 14),
      plot.title = element_text(hjust = 0.5, size = 15),
      axis.text.x = element_text(size = 11), # axe size
      axis.text.y = element_text(size = 11), # axe size
      axis.title = element_text(size = 12)
    ) +
    labs(
      x = "k-NN seach",
      y = "time/s",
      title = "Query time for k-NN search",
      color = "solver",
    ) +
    annotate("text", x = 3.3, y = 0.55, label = "X", size = 12) +
    scale_fill_grey()
  return(plt)
}
t <- read.csv("../data/knn.csv")
g <- plot(t, "ss_varden", "name")
ggsave("figures/knn.pdf", width = 10, height = 8, dpi = 1800)
``````
